Template Master's Thesis

### 2023-08-16 paper.tex
Update analysis section

For this clustering heuristic, we analyze the transaction data of the addresses, focusing on the transaction's ``calldata``. The first four bytes of the calldata represent the selector of the function signature, which specifies the smart contract function to be invoked. \newline
\textit{First}, we query all transactions that begin with a function signature related to the approval functions corresponding to ERC-20, ERC-721 and ERC-1155 token standards. This step helps us identify all approval transactions. \newline
\textit{Second}, we extract the approved address (spender address), which is always located at the same position within the calldata due to token standardization. We then record the spender address in a new field within our dataframe. \newline
\textit{Third}, we implement two filters on the approval transactions. The first filter checks if the spender address is part of our address set, and the second ensures that the spender address is different from the address initiating the transaction, thus eliminating self-approvals, which may occur due to a user interface bug or testing transactions. \newline
\textit{Fourth}, we group the remaining approvals by the initiating address and proceed to form the clusters.

We identified 16 clusters across 126 self-authorizing transactions, comprising 115 distinct addresses. After manual inspection, we excluded a cluster containing 80 addresses that had all approvals issued by the same address for the same token contract. The token contract represents a collection of wearable NFTs on Polygon called ``Renaissance King by René Mäkelä`` and may use an uncommon or potentially even faulty token minting scheme. \newline Ultimately, we discovered 35 addresses associated with 15 distinct entities.

\subsection{Node embeddings}
As described in previous sections, we tested different datasets to create the network graph using our ENS address pairs as ground truth. Der Approach ist zwar stark an Beres angelehnt, jedoch wendet er es an um pairs of deposit und withdrawal addressen zu clustern.

We found the intra-set asset transfers to perform best in terms of the average rank of a target address. 
Create network graph
Run ten separate experiments and calculate the average rank for each target address. The results of this are shown in Table X. Explain table, NaN values, within 5 nearest neighbors etc.

%1. Show that we tested different datasets to build network graph, best performing was intra-set asset transfers\\
%2. Evaluated the performance by average rank for the three methods, show results, describe how this method may be flawed/ why maybe not ideal\\

@@

3. Show how we clustered addresses using a treshold of euclidean distance, describe and visualize clustering results (histograms) \\
4. Describe two step approach test, may need further research and would be ideal to incorporate into node embedding feature vectors \\

@@

@@

\section{Discussion}
Discuss which approach worked best for clustering a predefined address set
A reference implementation for clustering a predefined address set using node embeddings on Github

@@

>>>>

To find self-authorization, we analyze the transaction data of the addresses, focusing on the transaction's ``calldata``. The first four bytes of the calldata represent the selector of the function signature, which specifies the smart contract function to be invoked. \newline
\textit{First}, we query all transactions that begin with a function signature related to the approval functions corresponding to ERC-20, ERC-721 and ERC-1155 token standards. This step helps us identify all approval transactions. \textit{Second}, we extract the approved address (spender address), which is always located at the same position within the calldata due to token standardization. We then record the spender address in a new field within our dataframe. \textit{Third}, we implement two filters on the approval transactions. The first filter checks if the spender address is part of our address set, and the second ensures that the spender address is different from the address initiating the transaction, which may occur due to a user interface bug or testing transactions. \textit{Fourth}, we group the remaining approvals by the initiating address and proceed to form the clusters.

We identified 16 clusters across 126 self-authorizing transactions, comprising 115 distinct addresses. After manual inspection, we excluded a cluster containing 80 addresses that had all approvals issued by the same address for the same token contract. The token contract represents a collection of wearable NFTs on Polygon called ``Renaissance King by René Mäkelä`` and may use an uncommon or potentially even faulty token minting scheme. Ultimately, we discovered 35 addresses associated with 15 distinct entities.

\subsection{Node embeddings}

Our analysis of node embedding methods starts with a network graph built from intra-set asset transfers. We treat addresses as nodes and add undirected edges between them if they interacted with each other. \newline
To use the Python library developed by \cite{karateclub}, we remove multi-edges and loops (transfers with same sender and recipient address) and only consider nodes within the largest connected component. The resulting network graph includes 51,566 nodes and 249,302 edges. As previously stated, we utilize the Diff2Vec, Role2Vec and DeepWalk methods from the library. \newline
Subsequently, we run ten independent experiments for each method. Our choice of input parameters is identical to \cite{Beres2020}. Each experiment returns a node embedding in the form of a matrix with 51,566 rows corresponding to the number of nodes in the graph, and 128 columns, representing the feature vector dimensions. \newline
For any node within the embedding, we can easily order all other nodes (addresses) by the Euclidean distance. %We can easily order nodes by the Euclidean distance to a given node. 
We achieve this through the Faiss library, suitable for efficient similarity search and clustering of dense vectors.  \newline
This enables us to search for our ENS ground truth pairs and report their relative rank. The results for each address pair, averaged over ten experiments are presented in Table \ref{tbl:ENS_Domain_Ranks}. Additionally, we calculated the mean, median, standard deviation and the rate of the target address appearing within the five or ten nearest neighbors for each method. \newline
All three methods demonstrated remarkable efficacy in locating the target address, which indicates their ability to find multiple addresses controlled by a single entity. %Ability to assign highly similar feature vectors to both addresses within a ground truth pair.
Role2Vec seems to be the most effective method, with the target address, on average, being found within the 28 nearest neighbors. In contrast, Diff2Vec and DeepWalk produced slightly higher averages of 46 and 62, respectively.
Furthermore, Role2Vec found the target address within the five nearest neighbors in 19 of 34 cases and within the ten nearest neighbors in 71\% of cases.
Despite the findings of \cite{Beres2020}, it appears that Diff2Vec is slightly less effective than Role2Vec or DeepWalk, although it is still generally successful. \newline
It is noteworthy that two address pairs are not included in the network graph and therefore display no values. However, they have been included to demonstrate that the intra-set asset transfer approach may not always be applicable to cluster all addresses of a predefined set. \newline
We also need to consider, that average rank may not be the most appropriate evaluation metric, particularly when a user controls significantly than two addresses. For example, if a single entity controls 20 addresses. Only one pair of addresses is detected as ground truth. Even if the algorithm finds all 20 addresses within the nearest neighbors but identifies our ground truth pair as the last one, we will score it lower than another algorithm that finds only one of the twenty addresses but within, for example, the ten nearest neighbors.

%We can say that for these address pairs, the methods are all surprisingly good in finding the target address -> node embedding methoden schreiben den beiden addressen/nodes sehr ähnliche feature vectoren zu.
%Role2Vec seems to work best out of the three, it has the lowest mean (28) and standard deviation and almost the same median as deepwalk.
%In contrast to Beres, where diff2vec worked best, in our case it is slightly less good then the other methods but still good overall.
%Average rank may not always be the best method, since a user can control more than two addresses. Make example: If someone has 20 addresses and all are found within the twenty nearest neighbors, but our address pairs only has found the twentieth address as a ground truth pair.
%Since we have Random guess would yield an average of 25k. Maximum is 51,566.

%As described in previous sections, we tested different datasets to create the network graph using our ENS address pairs as ground truth. Der Approach ist zwar stark an Beres angelehnt, jedoch wendet er es an um pairs of deposit und withdrawal addressen zu clustern. We found the intra-set asset transfers to perform best in terms of the average rank of a target address.

@@

After evaluating the different node embedding methods, we want to cluster addresses to assess the number of entities represented by the 51,566 nodes in the network/addresses. %to make a statement about the real number of users 
One approach might involve assigning the $k$ nearest neighbours of a node to a cluster and subsequently merging clusters until each node is assigned to exactly one cluster. However, selecting an appropriate $k$ is challenging, and it is hard to make the case that each address should belong to a cluster of $k$/ that each entity uses at least $k$ addresses.
Instead, we choose to build clusters based on a Euclidean distance treshold value. All neighbors of a node that fall below this treshold are considered a cluster. Subsequently, we merge overlapping clusters; for instance, if node A is clustered with nodes B and C, and node C is clustered with X, we form a cluster comprising A, B, C, and X.
We explored various treshold values and visualized the resulting cluster sizes in a histogram. %to better understand the distribution

%4. Describe two step approach test, may need further research and would be ideal to incorporate into node embedding feature vectors \\

@@

Intra-token-transfer events -> select all LAND transfers -> report the transaction hash\\
find all transfer events and transactions for the list of transaction hashes, drop duplicates, combine transactions and token transfers\\
Detect purchases, report in new column\\
Filter for simple transfers, build clusters\\
Visualization

@@

\section{Discussion}

%The results chapter or section simply and objectively reports what you found, without speculating on why you found these results. The discussion interprets the meaning of the results, puts them in context, and explains why they matter.

%discussion is an in-depth exploration of the results, going into detail about the meaning of your findings and citing relevant sources to put them in context.

%Discussion section: (a) Try to explain "What do your results mean?", and (b) how they relate to the literature,

Discuss which approach worked best for clustering a predefined address set and why.

%A reference implementation for clustering a predefined address set using node embeddings on Github

Limitations

@@

%The conclusion is more shorter and more general: it concisely answers your main research question and makes recommendations based on your overall findings.
%Conclusions section: Re-state the main points in a new concise way that you want your readers to remember.
